### 2018-06-18 FrascatiPlot/Paper/NucleiB2.tex
updates to text

\centering
\begin{tabularx}{\textwidth}{cccccccc}
%\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} 
 \hline \hline
\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & Spin $J$ & \makecell{(charge) \\rms\\ radius (fm)} &  \makecell{harmonic \\ oscillator \\ width \\r (fm) } & Refs. \\ \hline
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}      \\ \hline
\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &             &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &              &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &            & \cite{Davis:2005mb,Nemura:1999qp} \\ \hline
\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &             & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8                       &                 & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1                      &           &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8                     &            & \cite{Davis:2005mb,Nemura:1999qp}\\ \hline \hline
\end{tabularx}
\caption{Properties of nuclei and hyper-nuclei. $B_{E}$ is the binding energy in MeV. The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction. The size parameter $r$ of the wave-function of the harmonic oscillator potential is chosen such that the measured/expected rms is approximately reproduced (see text for details). References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
\label{tab:nucleusradii}
\end{table}

@@

\textcolor{red}{In particular, we approximate the wave-function of the objects under study by the wave-function of a spherical harmonic oscillator as in~\cite{Scheibl:1998tk}. This allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions. In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter $r$ of the harmonic oscillator potential. We encourage future more rigorous studies which address the coalescence probabilities with more realistic wave-functions. Consider mentioning the further  approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}
In this approach, the quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$. In the case of the deuteron, the quantum mechanical correction factor $\langle C_{d} \rangle$ has been approximated as

\begin{equation}
\langle C_{d} \rangle \approx \frac{1}{\left[1+ \left(\frac{\dradius}{2R_{\perp}(m_{T})}\right)^{2}\right] \sqrt{1+ \left(\frac{\dradius}{2R_{\|}(m_{T})}\right)^{2}}}
\label{eq:Cd}
\end{equation}
%
where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lenghts of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
The size of the nucleus enters in the determination of the coalescence parameter \btwo~via the quantum-mechanical correction factor $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})}
\label{eq:B2cd}
\end{equation}
%
which is the main result of \cite{Scheibl:1998tk}. It is interesting to note that the coalescence parameter decreases with increasing volume, as expected. In addition to this, the quantum mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size in the calculation of \btwo, which reflects the coalescence probability. 
If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to 
\begin{equation}
\langle C_{d} \rangle \approx \left[1+ \left(\frac{\dradius}{2R(m_{T})}\right)^{2}\right]^{-3/2}
\label{eq:Cdapprox}
\end{equation}
%
and
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}R^{3}(m_{T})}.
\label{eq:B2approx}
\end{equation}
%
Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo (on the right), calculated assuming (a.) a point-like nucleus, (b.) $\dradius = 0.3$ fm as currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the current estimate of the rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm. 
As can be seen in Fig. \ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.

>>>>

\centering
\begin{tabularx}{\textwidth}{cccccccc}
%\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} 
 \hline \hline
\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & Spin $J$ & \makecell{(charge) \\rms\\ radius (fm)} &  \makecell{harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs. \\ \hline
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}      \\ \hline
\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &             &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &              &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &            & \cite{Davis:2005mb,Nemura:1999qp} \\ \hline
\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &             & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8                       &                 & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1                      &           &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8                     &            & \cite{Davis:2005mb,Nemura:1999qp}\\ \hline \hline
\end{tabularx}
\caption{Properties of nuclei and hyper-nuclei. $B_{E}$ is the binding energy in MeV. The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction. The size parameter $r$ of the wave-function of the harmonic oscillator potential is chosen such that the measured/expected rms is approximately reproduced (see text for details). References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
\label{tab:nucleusradii}
\end{table}

@@

In particular, the wave-function of the objects under study are approximated by the wave-function of a spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$. For the deuteron (A = 2) wave-function $\varphi_{d}(\vec{r}) $, one obtains

\begin{equation}
 \varphi_{d}(\vec{r}) = (\pi r_{d}^2)^{-3/4} \exp\left(-{r^2 \over 2 r_{d}^2}\right) \;.
\end{equation}

\noindent For larger nuclei (A > 2), analogous forms exist (see for instance~\cite{Scheibl:1998tk} for the explicit form of A=3). The relation between the characteristic size parameter $r_{A}$ and the rms of the wave-function was derived in~\cite{Shebeko:2006ud} as

\begin{equation}
 {\rm rms}_{A}^2 = {3 \over 2}{A - 1 \over A} r_{A}^2
\end{equation}

\noindent for point-like constituents. In particular, we obtain $r_{d}=\sqrt{4/3}{\rm rms}_{d}$ for A= 2, $r_{3}= {\rm rms}_{3}$ for A = 3, and ???????.

This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions. In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter $r_{A}$ of the harmonic oscillator potential. We encourage future more rigorous studies which address the coalescence probabilities with more realistic wave-functions. \textcolor{red}{Consider mentioning the further  approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}

In this approach, the quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$. In the case of the deuteron, the quantum mechanical correction factor $\langle C_{d} \rangle$ has been approximated as

\begin{equation}
\langle C_{d} \rangle \approx \frac{1}{\left[1+ \left(\frac{\dradius}{2R_{\perp}(m_{T})}\right)^{2}\right] \sqrt{1+ \left(\frac{\dradius}{2R_{\|}(m_{T})}\right)^{2}}}
\label{eq:Cd}
\end{equation}
%
where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
The size of the nucleus enters in the determination of the coalescence parameter \btwo~via the quantum-mechanical correction factor $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})}
\label{eq:B2cd}
\end{equation}
%
which is the main result of \cite{Scheibl:1998tk}. It is interesting to note that the coalescence parameter decreases with increasing volume, as expected. In addition to this, the quantum mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size in the calculation of \btwo, which reflects the coalescence probability. 
If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to 
\begin{equation}
\langle C_{d} \rangle \approx \left[1+ \left(\frac{\dradius}{2R(m_{T})}\right)^{2}\right]^{-3/2}
\label{eq:Cdapprox}
\end{equation}
%
and
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}R^{3}(m_{T})}.
\label{eq:B2approx}
\end{equation}
%
Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo (on the right), calculated assuming (a.) a point-like nucleus, (b.) $\dradius = 0.3$ fm as currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the current estimate of the rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm. 
As can be seen in Fig. \ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.
